---
title: "Modern Infectious Disease Epidemiology (MIDE) course website"
output: 
  html_document:
    toc: FALSE
---

```{r, include = FALSE}
#just so I can use emoticons
#devtools::install_github("hadley/emo")
library(emo)
```

**This website is under construction for a course I'll be teaching in Fall 2020. As long as you see this message, expect things to not really work `r emo::ji('smiley')`.**


Welcome to the Modern Infectious Disease Epidemiology (MIDE) course website. 

This website contains content for the online course _EPID 8510 - Dynamical Systems Approach to Infectious Disease Epidemiology_ taught in Fall 2020 at the University of Georgia by [Andreas Handel.](https://www.andreashandel.com/) Most materials are hosted here, some are on external sites and either linked or embedded from here.

I plan to keep this website continuously online, with updates happening every time I teach the course again.


# Website content

The __General Information__ section provides a class __Syllabus__ and a __Schedule__. The latter will likely be updated throughout the course, so check it regularly.

The majority of the content is listed under the __Modules__ heading. Each module has several units in a drop-down/pop-out menu. Go through them in the listed order.

Instructions for specific exercises are listed in the __Exercises__ section. You will be told when you should access those documents and do the exercises. Of course, reading ahead is allowed `r emo::ji('smiley')`.

The course includes a semester-long project. Instructions and detailed information for this are given in the __Project__ section.

The __Communication__ section provides information on how course communications are planned to happen.

The __Resources__ section contains a listing of external materials. Some of this material will assigned as part of this course. You will be told what exactly to read or work through in the modules documents. Other resources are listed in case you might find them helpful. All materials are (should be) available freely online.

Note that by default, all links open in the current tab. You'll likely want external ones to open in a separate tab or window. To do so, you can (with most browsers) hold the `Ctrl` button when clicking, or do a right-click and select `open in new tab/window`.


# Additional Notes

Some additional comments for UGA students: 
* While the course's official title at UGA is _Dynamical Systems Approach to Infectious Disease Epidemiology_, I think it's too much of a mouthful and I don't like that title much anymore, so I'll just be referring to the course as _MIDE -  Modern Infectious Disease Epidemiology_.
* Announcements, discussions and all other communication will happen through Slack.
* We will not be using eLC.



# Getting started

I suggest you start by looking over the __Syllabus__ and __Schedule__ documents, then __Communication__ and __Resources__. After that, start with the __Module 1__ content in the given order. You can read through the _Project_ section early or wait until you have gone through at least modules 1 and 2.

## Acknowledgements

This course was developed and is maintained by [Andreas Handel](https://www.andreashandel.com/).

```{r, results = "asis", echo = FALSE, message = FALSE}
#the following code snipped is taken from Hadley's R4DS intro page
library(dplyr)
contributors <- readr::read_csv("contributors.csv", col_types = list())
contributors <- contributors %>% 
  mutate(
    link = glue::glue("[\\@{login}](https://github.com/{login})"),
    desc = ifelse(is.na(name), link, glue::glue("{name} ({link})"))
  )
cat("The following individuals have contributed to improving the course:\n")
cat(paste0(contributors$desc, collapse = ", "))
```

The materials are licensed under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.](http://creativecommons.org/licenses/by-nc-sa/4.0/).


  
