---
title: "Infectious Disease Epidemiology <br> (Ecology)(Evolution) <br> - A model-based approach (IDEMA)"
output: 
  html_document:
    toc: FALSE
---

```{r, include = FALSE}
#just so I can use emoticons
#devtools::install_github("hadley/emo")
library(emo)
```


<!-- Some trickery to get the logo to show -->

<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"media/idema_logo.png\" style=\"float: right; border: none; width: 150px;\"/>')
   });
</script>


Last update/recompile: `r Sys.time()`


Welcome to the website for the course **Infectious Disease Epidemiology(Ecology)(Evolution) - A model-based approach (IDEMA).** 

This website contains content for an online course taught in Fall 2020 at the University of Georgia by [Andreas Handel.](https://www.andreashandel.com/) Most materials are hosted here, some are on external sites and either linked or embedded from here.

The course has finished, but the website will remain continuously online, with likely larger updates happening every time I teach the course again and minor ones in between.


# Website content

The __General Information__ section provides a class __Syllabus__ and a __Schedule__. The latter will likely be updated throughout the course, so check it regularly.

The majority of the content is listed under the __Modules__ heading. Each module has several units in a drop-down/pop-out menu. Go through them in the listed order. Modules will become available as the course progresses.

The course includes a semester-long project. Instructions and detailed information for this are given in the __Project__ section.

The __Communication__ section provides information on how course communications are planned to happen.

The __Resources__ section contains a listing of external materials. Some of this material will be assigned as part of this course. You will be told what exactly to read or work through in the modules documents. Other resources are listed in case you might find them helpful. All materials are (should be) available freely online, unless otherwise stated.


<!-- # Notes for UGA students -->

<!-- * The course's official title in the UGA system is _EPID 8510 - Dynamical Systems Approach to Infectious Disease Epidemiology_. Since I created the course, I decided that I don't like this title much anymore, it's a mouthful and too technical. I'll just be referring to the course as _IDEMA_. At some point, I'll get around to officially changing the title in the system (this is harder than you might expect).  -->
<!-- * We will not be using eLC. -->
<!-- * Announcements, discussions and all other communication will happen through Slack. You will get an invite to the class-specific Slack workspace by email. The email will come to your UGA account (the one that is listed in the class roster). If you can't join the Slack workspace for some reason, let me know. -->



# Getting started

I suggest you start by looking over the __Syllabus__ and __Schedule__ documents, then __Communication__ and __Resources__. After that, start with the __Module 1__ content in the given order. You can read through the _Project_ section to get an idea of what's coming.

## Acknowledgements

This course was developed and is maintained by [Andreas Handel](https://www.andreashandel.com/).

```{r, results = "asis", echo = FALSE, message = FALSE, warning=FALSE}
#the following code snipped is taken from Hadley's R4DS intro page
library(dplyr)
contributors <- readr::read_csv("IDEMACoursecontributors.csv", col_types = list())
contributors <- contributors %>% 
  mutate(
    link = glue::glue("[\\@{GithubID}](https://github.com/{GithubID})"),
    desc = ifelse(is.na(LastName), link, glue::glue("{FirstName} {LastName} ({link})"))
  )
cat("The following individuals have contributed to improving the course:\n")
cat(paste0(contributors$desc, collapse = ", "))
```


The materials are licensed under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.](https://creativecommons.org/licenses/by-nc-sa/4.0/) Linked and embedded materials are governed by their own licenses. I assume that all external materials used or embedded here are covered under the educational fair use policy. If this is not the case and any material displayed here violates copyright, please let me know and I will remove it. 


  
